\documentclass[margin]{res}  

\usepackage{hyperref}
\usepackage{enumitem}
% \usepackage{paralist}
\usepackage{comment}
\usepackage[dvipsnames]{xcolor}
\newcommand\myshade{85}
\colorlet{mylinkcolor}{blue}
\definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
\hypersetup{
  linkcolor  = darkcerulean,
  citecolor  = darkcerulean,
  urlcolor   = darkcerulean,
  colorlinks = true,
}

\newcommand{\field}[2]{\noindent \textbf{#1} \hfill #2 \\}
\newcommand{\uf}[2]{\noindent \textbf{#1} \hfill \url{#2} \\}
\newcommand{\uff}[2]{\item[--] #1 \\ \url{#2}}
\newcommand{\alphabeticalorder}[0]{\ensuremath {^{\alpha \beta}}}
\newcommand{\scheduled}[0]{\ensuremath {^\dagger}}
\newcommand{\presentedbycoauthor}[0]{\ensuremath {^{\star}}}
\newcommand{\specialurl}[2]{\href {#2} {\texttt{[#1]}}}
\newcommand{\preprint}[1]{\specialurl {preprint} {#1}}
\newcommand{\code}[1]{\specialurl {code} {#1}}
\newcommand{\data}[1]{\specialurl {data} {#1}}
\newcommand{\talk}[1]{\specialurl {talk} {#1}}
\newcommand{\slides}[1]{\specialurl {slides} {#1}}
\newcommand{\poster}[1]{\specialurl {poster} {#1}}
\newcommand{\paper}[1]{\specialurl {paper} {#1}}
\newcommand{\workshop}[1]{\specialurl {workshop} {#1}}
\newcommand{\authorref}[1]{\underline {\textbf{#1}}}
\newcommand{\news}[1]{\specialurl {news} {#1}}
\newcommand{\authorme}{\authorref{Marios Papachristou}}
\newcommand{\bemph}[1]{\textbf{\emph{#1}}}

% Increase text height
%\textheight=700pt

\begin{document}

%------------------------------------X-------------------------------------------
%    NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{\textbf{Marios Papachristou}}

\begin{resume}

\section{Contact \\ Information} 
E-mail \hfill \url{papachristoumarios@cs.cornell.edu} \\
GitHub \hfill \href{http://github.com/papachristoumarios}{\nolinkurl{papachristoumarios}} \\
Office \hfill 302 Gates Hall, Cornell University, 107 Hoy Rd \\
Google Scholar \hfill \specialurl{profile}{https://scholar.google.gr/citations?user=T12JO3MAAAAJ&hl=en} \\
Twitter \hfill \href{https://twitter.com/papachristoum}{\nolinkurl {@papachristoum}} \\
Website \hfill \href{https://papachristoumarios.github.io}{\nolinkurl {papachristoumarios.github.io}}

\section{Areas} Algorithms, Information Networks, Machine Learning, Data Mining
% \emph{Foci:} Statistical Modeling of Networks, Financial Networks, Graph ML 

\section{Education}
\field {Cornell University} {\emph{2020 -- exp. 2026}}
Ph.D. in Computer Science, Minor: \emph{Applied Mathematics}
\begin{itemize}[nosep]    
\item[--] \emph{Advisor:} Jon Kleinberg
%\emph{Committee:} Jon Kleinberg, Emma Pierson, Sid Banerjee 
\item[--] \emph{Relevant Coursework:} Analysis of Algorithms, Information Networks, Numerical Methods for Data Science, Design of Online Marketplaces, ML Theory
\end{itemize} 

M.S. in Computer Science \hfill {\emph{2020 -- 2022}}
 
\field{National Technical University of Athens}  {\emph{2015 -- 2020}} 
Diploma in Electrical and Computer Engineering (\emph{top 2\%}). Major: \emph{Computer Science}.
\begin{itemize}[nosep]
\item[--] \emph{Advisor:} Dimitris Fotakis

\end{itemize} 

\section{Refereed Publications\\ {
\footnotesize
\textup{\href{https://scholar.google.gr/citations?user=T12JO3MAAAAJ&hl=en}{Google Scholar Profile}} \\\alphabeticalorder  = \textup{alphabetical order} \\ $*$ = \textup{equal contribution}
}}

% See  for the full list. \medskip

\begin{enumerate}[nosep, label={[P\arabic*]}]    
 
   \item \authorme, Sid Banerjee, Jon Kleinberg. ``Dynamic Interventions for Networked Contagions''. \emph{ACM Web Conference (WWW) 2023}. \\
		\preprint{https://arxiv.org/abs/2205.13394} \code{https://github.com/papachristoumarios/dynamic-clearing} \poster{https://drive.google.com/file/d/1l0TCsoZNo3NoOOHsPSh1ofctXD4ivFir/view?usp=sharing}
		\paper{https://dl.acm.org/doi/abs/10.1145/3543507.3583470}
		\slides{https://drive.google.com/file/d/1ZZ6F6PFNsBjYKFyurkwM2IbenuzXJEAs/view?usp=share_link}


   \item \authorme, Jon Kleinberg. ``Core-periphery Models for Hypergraphs''. \emph{ACM SIGKDD Intl. Conf. on Knowledge Discovery and Data Mining (KDD) 2022.} \\
   \paper{https://arxiv.org/abs/2206.00783} \code{https://doi.org/10.5281/zenodo.5965849} \data{https://doi.org/10.5281/zenodo.5943043} \slides{https://drive.google.com/file/d/1k9pjPaeDtg7jhUivjlEmyunimcUb-DxL/view?usp=sharing} \poster{https://drive.google.com/file/d/1RJ3C7KKhTemfj5OBAiEXUHMVp-TJhTDs/view?usp=sharing}
   \item  \authorme, Jon Kleinberg. ``Allocating Stimulus Checks in Times of Crisis''. \emph{ACM Web Conference (WWW) 2022.} \\\preprint{https://arxiv.org/abs/2106.07560} \code{https://github.com/papachristoumarios/financial-contagion} \paper{https://doi.org/10.1145/3485447.3512047} \talk{https://youtu.be/WUmPBztK8Mo} \slides{https://drive.google.com/file/d/1v4v4jPOTzFtP8a5dhAFLoIjZSRDxAjBz/view?usp=sharing} \news{https://www.minneapolisfed.org/article/2022/social-policy-in-the-age-of-algorithms-an-interview-with-jon-kleinberg}   
   \item \authorme. ``Sublinear Domination and Core--periphery Networks''. \emph{Scientific Reports (Nature)}, 2021. \\ \paper{http://www.nature.com/articles/s41598-021-94105-8} \code{https://bit.ly/3wKNGI0} 
    \item \alphabeticalorder Apostolos Chalkis, Vissarion Fisikopoulos, \authorme, Elias Tsigaridas. ``Truncated Log-concave Sampling for Convex Bodies with Reflective Hamiltonian Monte Carlo''.   \emph{ACM Transactions on Mathematical Software (TOMS)}, 2023. This paper incorporates and supersedes our previous \href{https://arxiv.org/abs/2102.13068}{preprint}. \\ \paper{https://doi.org/10.1145/3589505} \code{https://github.com/GeomScale/volume_approximation}
    \item \authorme. ``Software clusterings with vector semantics and the call graph''. \emph{ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE) 2019}. \\ \paper{https://dl.acm.org/citation.cfm?id=3342483} \code{https://github.com/papachristoumarios/sade} \data{http://doi.org/10.5281/zenodo.2652487} \\\textbf{\emph{(ESEC/FSE Student Research Competition Finalist Paper)}}
    \item Vasilis Kostakis*, and \authorme*. ``Commons-based peer production and digital fabrication: The case of a RepRap-based, Lego-built 3D printing-milling machine''. \emph{Telematics and Informatics}, 2014. \\ \paper{https://bit.ly/2JRoisV} 
    
\end{enumerate}

\section{Working Papers}


\begin{enumerate}[nosep, label={[W\arabic*]}]  
   \item \authorme, Yuan Yuan. ``Network Formation and Dynamics among Multi-LLMs''. \emph{Under review}. 2024. \\
   		\preprint{http://arxiv.org/abs/2402.10659} \slides{https://drive.google.com/file/d/13Qm_82D0WrkmN1LAv2AUmjcputMOdm_y/view?usp=drive_link}

   \item \authorme, Sid Banerjee, Jon Kleinberg. ``Optimal Resource Allocation for Remediating Networked Contagions''. \emph{R\&R in Management Science.} 2023.
   
   \emph{This paper extends our previous works in \href{https://doi.org/10.1145/3485447.3512047}{WWW 2022} and \href{https://arxiv.org/abs/2205.13394}{WWW 2023}}. \\
       \slides{https://drive.google.com/file/d/1DgOCnJ5Pf3Je-F7a-Adiy2TTZ7oZUbbB/view?usp=sharing}

   \item \authorme, Longqi Yang, Chin-Chia Hsu, ``Leveraging Large Language Models for Collective Decision-Making''. \emph{Under review.} 2023. \\
  	\preprint{https://arxiv.org/abs/2311.04928}

   \item \authorme, Amin Rahimian. ``Group Decision-Making among Privacy-aware Agents''. \emph{Under review.} 2023. \\
  	\emph{Preliminary version accepted at the AAAI Workshop on Privacy-Preserving Artificial Intelligence.} 2023. \\
  		\preprint{https://arxiv.org/pdf/2402.08156.pdf} \poster{https://drive.google.com/file/d/149A7tdByRdOGHo_Xa_9H55qxExtESVhJ/view?usp=drive_link}

   \item \authorme, Amin Rahimian. ``Differentially Private Distributed Estimation and Learning''. \emph{Under review.} 2023. \\
   	   \preprint{https://arxiv.org/abs/2306.15865} \code{https://github.com/papachristoumarios/dp-distributed-estimation} \poster{https://drive.google.com/file/d/149A7tdByRdOGHo_Xa_9H55qxExtESVhJ/view?usp=drive_link}
   	   
   \item \authorme, Amin Rahimian. ``Production Networks Resilience: Cascading Failures, Power Laws and Optimal Interventions''. \emph{Under review.} 
   		\emph{Preliminary poster presented at the ACM Conference of Economics and Computation (EC).} 2023. \\ \preprint{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4392226} \code{https://github.com/papachristoumarios/supply-chain-resilience} \slides{https://drive.google.com/file/d/13kgKnjTHyO8j4BOJVykWwt43hSt3JrLw/view?usp=drive_link}
 
   \item \authorme, Rishab Goel, Frank Portman, Matt Miller, Rong Jin. ``GLINKX: A Scalable Unified Framework for Homophilous and Heterophilous Graphs''. \emph{Under Review}. 2023 \\\emph{Preliminary version presented at NeurIPS workshop on Graph Learning Frontiers (GLFrontriers)}, 2022. \\ \preprint{https://arxiv.org/abs/2211.00550} \poster{https://drive.google.com/file/d/14LwkvoH7sUe6qGvINGqTuMSHid16J3Av/view?usp=share_link} \workshop{https://openreview.net/forum?id=GlViaJSwnlK}
    \item \authorme, Dimitris Fotakis. ``Stochastic Opinion Dynamics for User Interest Prediction in Online Social Networks''.  \emph{Preprint}, 2020. \\ \preprint{https://www.researchgate.net/publication/353006940_Stochastic_Opinion_Dynamics_for_Interest_Prediction_in_Social_Networks}
\end{enumerate}


\section{Research \\ Experience}

 \textbf{Applied Research Intern -- Microsoft} \hfill \emph{May 2023 -- August 2023}

\begin{itemize}[nosep]
	\item[--] Large Language Models (LLMs) for collective intelligence. 	
	\item[--] \emph{Office of Applied Research, with Chin-Chia Hsu and Longqi Yang}
\end{itemize}


\textbf{Engineering Intern -- Twitter} \hfill \emph{May 2022 -- August 2022}
\begin{itemize}[nosep]
\item[--] Scalable Graph Machine Learning on graphs. 
\item[--] \emph{User Modeling Research, with Rishab Goel, Frank Portman, and Matthew Miller}
\end{itemize}

\textbf{Graduate Researcher -- Cornell University} \hfill \emph{Sept. 2020 -- ongoing}
\begin{itemize}[nosep]
	\item[--] Research in social and information networks, (allocation algorithms to mitigate contagion in financial and supply-chain networks, statistical graph and hypergraph models)
\end{itemize}


\textbf{Researcher -- GeomScale Organization} \hfill \emph{May 2020 -- March 2020}

\begin{itemize}[nosep]
	\item[--] Part-time research on sampling from truncated log-concave densities, and convex optimization, working on the \href{https://github.com/GeomScale/volesti}{volesti} open-source package.
	\item[--] \emph{Mentors:} Apostolos Chalkis, Vissarion Fisikopoulos, Elias Tsigaridas
\end{itemize}


\textbf{Researcher -- Athens University of Economics and Business} \hfill \emph{2018 -- 2020}
\begin{itemize}[nosep]
\item[--] Software architecture recovery via call graphs, source code embeddings, and clustering methods.
\item[--] \emph{Mentor: Diomidis Spinellis}
\end{itemize}

\textbf{Google Summer of Code 2020 (GeomScale)}  \hfill \emph{June 2020 -- August 2020}
\begin{itemize}[nosep]
\item[--] \emph{Project: Sampling from high-dimensional truncated log-concave densities.} \\ \code{https://GeomScale/volesti} \specialurl{talk1}{https://www.youtube.com/watch?v=P7YfC8Nn6sY} \specialurl{talk2}{https://www.cs.utah.edu/~jeffp/WaGoML/index.html}
\end{itemize}

\textbf{Google Summer of Code 2018 (GFOSS-OTA)}  \hfill {\emph{April 2018--September 2018}}
\begin{itemize}[nosep]
\item[--] \emph{Project: 3gm}. Automated codification of Greek Legislation. \\ \code{https://github.com/eellak/gsoc2018-3gm} \data{https://archive.org/details/greekgovernmentgazette} \talk{https://www.youtube.com/watch?v=_UIGsy85Ehw}
\end{itemize}

\textbf{Researcher -- P2P Lab}  \hfill {\emph{2013 -- 2014}}


%\textbf{Hellenic Center for Marine Research} \hfill \emph{June 2014 -- August 2014}

\section{Honors \& \\ Awards} 
\begin{itemize}[nosep]
	\item[--] Onassis Scholarship \hfill \emph{2023}
	\item[--] LinkedIn Ph.D. Fellowship (14.8\% acceptance rate) \hfill \emph{2022} 	
	\item[--] Gerondelis Scholarship \hfill \emph{2022}
	\item[--] A.G. Leventis Scholarship (12.5\% acceptance rate) \hfill \emph{2022}
	\item[--] Chateaubriand Fellowship \emph{(declined)} \hfill \emph{2022}
	\item[--] Cornell Fellowship \hfill \emph{2020}
	\item[--] Thomaidion Award \hfill \emph{2019}
	\item[--] ESEC/FSE 2019 ACM Student Research Competition Finalist \hfill \emph{2019}

	\item[--] 4th (out of 93) in International Space Engineering  Competition (CanSat) \hfill \emph{2019}
    \item[--] 2nd Award at the \emph{``be finnovative 2.0 accelerator''} \hfill \emph{2018}
   	\item[--] 1st Award at \emph{``Crowdhackathon Fintech \#2''} \hfill \emph{2017}
   	\item[--] Top \%1 worldwide in IEEEXtreme 11.0 Programming Competition \hfill \emph{2017}
    \item [--] Touramanoglu Scholarship \hfill \emph{2015}
    \item [--] ``The Great Moment of Education'' Scholarship \hfill \emph{2015}

\end{itemize}

\section{Teaching \\ Experience} 
\begin{itemize}[nosep]
	\item[--] The Structure of Information Networks (PhD-level, Cornell) \hfill \emph{Spring \& Fall 2023} 
    \item[--] Discrete Mathematics (NTUA) \hfill \emph{Spring 2017}
    \item[--] Programming Techniques (NTUA) \hfill \emph{Spring 2016}
    \item[--] Introduction to Computer Programming (NTUA) \hfill \emph{Fall 2016, Fall 2017}
\end{itemize}


\section{Talks \& \\ Presentations \\
\footnotesize
\scheduled  = \textup{scheduled} \\ \presentedbycoauthor = \textup{presented by co-author}
}

\begin{itemize}[nosep]
	
	\item \bemph{Information aggregation and distributed learning in privacy-critical environments}
	\begin{itemize}[nosep]
	\item Rutgers University, Seminar\presentedbycoauthor \hfill \emph{November 2023}	
	\end{itemize}

	\item \bemph{Leveraging Large Language Models for Collective Decision-Making}
	\begin{itemize}[nosep]
		\item Microsoft Research, Invited Applied Research Talks \hfill \emph{August 2023}
	\end{itemize}

	\item \bemph{Production Networks Resilience: Cascading Failures, Power Laws, and Optimal Interventions}
	\begin{itemize}[nosep]
		\item Columbia University, Student Theory Seminar \hfill \emph{November 2023}
		\item Cornell University, Theory Tea \hfill \emph{November 2023}
		\item INFORMS Annual Meeting\presentedbycoauthor \hfill \emph{October 2023}
		\item Cornell University, LinkedIn Campus Visit \hfill \emph{May 2023}
	\end{itemize}

	\item \bemph{Resource Allocation in a Financial Contagion Environment}
	\begin{itemize}[nosep]
		\item University of Chicago, Theory Seminar \hfill \emph{October 2023}
		\item Indiana University, Center for Complex Networks and Systems Research \\ \hfill \emph{September 2023} 
		\item Cornell University, CS 6850 Guest Lecture \hfill \emph{April 2023}
		\item Cornell University, Theory Seminar \hfill \emph{November 2022}
		% \item NTUA Theory Seminar
	\end{itemize}
	
	\item \bemph{Dynamic Interventions for Networked Contagions}
	\begin{itemize}[nosep]
		\item \emph{Invited Talk at} INFORMS Annual Meeting \hfill \emph{October 2023}
		\item ACM Web Conference \hfill \emph{April 2023}	
		\item ACM Conference on Equity and Access in Algorithms, Mechanisms, and Optimization \hfill \emph{October 2022}
	\end{itemize}

	\item \bemph{Core-periphery Models for Hypergraphs}
	\begin{itemize}[nosep]
		\item ACM Conference on Knowledge Discovery and Data Mining \hfill \emph{August 2022}
	\end{itemize}
	
	\item \bemph{GLINKX: A Scalable Unified Framework for Homophilous and Hetero\-philous Graphs}
	\begin{itemize}[nosep]
		\item NeurIPS Workshop on Graph Learning Frontiers  \hfill \emph{December 2022}
		\item Twitter, Machine Learning Seminar \hfill \emph{August 2022}
		
	\end{itemize}

 
	\item \bemph{Allocating Stimulus Checks in Times of Crisis} 
	\begin{itemize}[nosep]
		\item ACM Web Conference \hfill \emph{April 2022}
		\item ACM Conference on Equity and Access in Algorithms, Mechanisms, and Optimization \hfill \emph{October 2021}
	\end{itemize}

	\item \bemph{Sampling from Truncated High Dimensional Logconcave Densities}
	\begin{itemize}[nosep]
		\item PyData Global \hfill \emph{December 2020}
	\end{itemize}
	
	\item \bemph{Software Clusterings with Vector Semantics and the Call Graph}
	\begin{itemize}[nosep]
		\item ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering \hfill \emph{August 2019}
	\end{itemize} 
	
\end{itemize}

\section{Reviewing} 
%\begin{itemize}[nosep]
%
%\item [--] \emph{Program Committee.} \href{https://facctconference.org/2022}{FAccT `22}
%\item [--] \emph{Reviewer.} \href{https://kdd.org/kdd2023/}{KDD '23}, \href{https://2023.ecmlpkdd.org/}{ECML-PKDD '23}, \href{https://glfrontiers.github.io/overview/}{GLFrontiers@NeurIPS `22}, \href{https://joss.theoj.org/}{JOSS}, \href{https://sites.google.com/view/whmd2021}{WHMD@NeurIPS `21},  \href{https://www.springer.com/journal/291?gclid=Cj0KCQiAr5iQBhCsARIsAPcwROPwkZ2Nw4Ubg7i91Y2hITU4OE4lzk_56F09IS09b5wh-sMhuqgft0YaAgATEALw_wcB}{OR Spectrum}, \href{https://www.springer.com/journal/10994/}{Machine Learning}
%\item [--] \emph{Mentorship:} Google Summer of Code (2019--), Cornell Undergraduate AI Group (2022--), Student-applicant support program at Cornell CS (2022). 
%
%\end{itemize}

\begin{itemize}[nosep]
	\item \emph{Program Commitee}
	\begin{itemize}[nosep]
		\item ACM Conference on Fairness Accountability and Transparency (FAccT) \hfill \emph{2022}
		\item ACM Conference on Knowledge Discovery and Data Mining (KDD) \hfill \emph{2023}
	\end{itemize}
	\item \emph{Reviewing}
	\begin{itemize}[nosep]
		\item ACM Web Conference (WWW) \hfill \emph{2024}
		\item Innovations in Theoretical Computer Science (ITCS) \hfill \emph{2024}
		\item ACM Conference on Human Factors in Computing (CHI) \hfill \emph{2024}
		\item European Conference on Machine Learning and Principles and Practice of Knowledge Discovery in Databases (ECML-PKDD) \hfill \emph{2023}
		\item Machine Learning (Springer)
		\item NeurIPS 2022 Workshop on Graph Learning Frontiers (GLFrontiers) \hfill \emph{2022}
		\item NeurIPS 2021 Workshop on Human and Machine Decisions \hfill \emph{2021--} 
		\item Journal of Open Source Software \hfill \emph{2021--}
	\end{itemize}

\end{itemize}

	
\section{Mentorship \& Volunteering}
	
	
	\begin{itemize}[nosep]
		\item Student-applicant Support Program at Cornell CIS \hfill \emph{2022}
		\item Google Summer of Code Mentor \hfill \emph{2019--2022}
		\item Volunteer lessons for the National Olympiad of Informatics (PDP) and other programming competitions  \hfill \emph{2019}
	\end{itemize}
	

\section{Last Updated} \today


\end{resume}

\end{document}
